---
title: "Introduction to regr"
author: "Joe Vanderlans"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{regr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The goal of this package is to provide users the ability to easily replicate STATA regressions in R.  Particularly, this package provides the `reg` function, inspired by STATA's `reg` command.  This function allows users to quickly run regressions with robust or clustered standard errors and returns results which match those of STATA.  This document demonstrates how to use `regr`.

## Data

This example uses test data from Petersen (2006).  Petersen performs the following analyses on this data:

1. Standard OLS (`reg y x`)
1. Robust standard errors:  (`reg y x, robust`)
1. Cluster standard errors by firm (`reg y x, cluster(firmid)`)
1. Cluster standard errors by year (`reg y x, cluster(year)`)
1. Cluster standard errors by firm and year (`reg y x, cluster(firmid, year)`)

Petersen provides the results to these analyses using STATA [here](http://www.kellogg.northwestern.edu/faculty/petersen/htm/papers/se/test_data.htm).  We will replicate these analyses in turn to demonstrate the use of `regr`.

## Example Regressions

First, load the data.
```{r}
library(regr)
data("panel_data")
```

Now, we can run the regressions.

### 1. Basic OLS
```{r}
reg(y ~ x, panel_data)
```

### 2. Robust standard errors
```{r}
reg(y ~ x, robust = TRUE, panel_data)
```

### 3. Cluster standard errors by firm
```{r}
reg(y ~ x, cluster = "firmid", panel_data)
```

### 4. Cluster standard errors by year
```{r}
reg(y ~ x, cluster = "year", panel_data)
```

### 5. Cluster standard errors by both firm and year
```{r}
reg(y ~ x, cluster = c("firmid", "year"), panel_data)
```
